Employee Attrition: What makes an employee leave?

### 2017-10-19 LatexPaper/paper.tex
fixed < sign with $<$

\paragraph{The U.S. Office of Personnel Management (OPM) serves as the central Human Resources department for all Federal agencies, including the management of federal agency health insurance and retirement benefits. Their oversight of policy implementation as well as being a general resource for all agency Human Resource departments makes their employment data of particular interest for this paper. OPM releases on a quarterly basis updated separation data on its over two million federal civil service workers.  We used these anonymized data sets to create a full year of separation data, spanning October 2014 - September 2015.   These data [7], include the following variables: 1) age group, captured categorically in 5 year increments (AGELVL and AGELVLT), 2) agency type and subtype information (AGYTYP, AGYTYPT, AGY, AGYT, AGYSUB, and AGYSUBT), 3) gender (GENDER and GENDERT), 4) General Schedule Grade, or equivalent, dictating salary level (GSEGRD, 5) geographical location of the employee down to the state level (LOCTYP, LOCTYPT, LOC, LOCT), 5)length of service as a government employee captured in one year increments until five years was achieved, then every five after that (LOSLVL and LOSLVLT), 6)occupation type  in regards to white or blue collar, occupation family, and in some cases, down to the particular occupation itself (i.e. "chaplain") (OCCTYP, OCCTYPT, OCCFAM, OCCFAMT, OCC, OCCT), 7) occupation category among seven main categories (i.e. "Technical" and "Clerical")(PATCO and PATCOT), 8) pay plan and grade for both GSE and non-GSE occupations (PPTYP, PPTYPT, PPGROUP, PPGROUPT, PAYPLAN, PAYPLANT, and PPGRD), 9) salary range, captured categorically starting with < \$20,000 and followed in \$10,000 increments (SALLVL and SALLVLT), 10) reason for separation (SEP and SEPT), and 11) type of appointment and worschedules, denoting factors such as permanence, seasonality, and executive status (TOATYP, TOATYPT, TOA, TOAT, WSTYP, WSTYPT, WORKSCH, and WORKSCT).   }

>>>>

\paragraph{The U.S. Office of Personnel Management (OPM) serves as the central Human Resources department for all Federal agencies, including the management of federal agency health insurance and retirement benefits. Their oversight of policy implementation as well as being a general resource for all agency Human Resource departments makes their employment data of particular interest for this paper. OPM releases on a quarterly basis updated separation data on its over two million federal civil service workers.  We used these anonymized data sets to create a full year of separation data, spanning October 2014 - September 2015.   These data [7], include the following variables: 1) age group, captured categorically in 5 year increments (AGELVL and AGELVLT), 2) agency type and subtype information (AGYTYP, AGYTYPT, AGY, AGYT, AGYSUB, and AGYSUBT), 3) gender (GENDER and GENDERT), 4) General Schedule Grade, or equivalent, dictating salary level (GSEGRD, 5) geographical location of the employee down to the state level (LOCTYP, LOCTYPT, LOC, LOCT), 5)length of service as a government employee captured in one year increments until five years was achieved, then every five after that (LOSLVL and LOSLVLT), 6)occupation type  in regards to white or blue collar, occupation family, and in some cases, down to the particular occupation itself (i.e. "chaplain") (OCCTYP, OCCTYPT, OCCFAM, OCCFAMT, OCC, OCCT), 7) occupation category among seven main categories (i.e. "Technical" and "Clerical")(PATCO and PATCOT), 8) pay plan and grade for both GSE and non-GSE occupations (PPTYP, PPTYPT, PPGROUP, PPGROUPT, PAYPLAN, PAYPLANT, and PPGRD), 9) salary range, captured categorically starting with $<$ \$20,000 and followed in \$10,000 increments (SALLVL and SALLVLT), 10) reason for separation (SEP and SEPT), and 11) type of appointment and worschedules, denoting factors such as permanence, seasonality, and executive status (TOATYP, TOATYPT, TOA, TOAT, WSTYP, WSTYPT, WORKSCH, and WORKSCT).   }
